---
title: "Sample Quarto Document"
author: "Rohit Dutta"
date: "2022-09-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Welcome to this sample document**

### **Solving Quadratic Equations**

Consider the equations of the form $ax^2 + bx + c = 0$. This is a quadratic equation; changing the values of $a, b$ and $c,$ changes the shape of the quadratic. There are two solutions to a quadratic equation:

$$x = \dfrac{-b \pm \sqrt{b^2-4ac}}{2a}$$

Let's draw a quadraic curve for different values of $a, b$ and $c.$

```{r fig.align='center'}
a <- 10
b <- 3
c <- -5
x <- seq( -2, 2,length = 1e3)
fx <- a*x^2 + b*x + c
plot( x, fx, type = "l", xlab = "x", ylab = "quadratic function")
## adding line for solution 
abline(h = 0, lty = 2, col = "red")
```

In the above, we can also change the way the plot appears. I will rerun the above code, without
displaying the code, and only producing the plot of figure height “4” units and figure width
“4” units
```{r echo = FALSE, fig.height = 4, fig.width = 4, fig.align = 'center'}
 plot( x, fx, type = "l", xlab = "x", ylab = "quadratic function", sub = "Figure 1: A quadratic function")
 abline(h = 0, lty = 2, col = "red")
```



## **Studying the Cricket dataset**

We will study the cricket dataset more closely now. The battingbowling.csv file in your
repository contains information regarding various potential all-rounders in men’s ODI cricket.
The players’ batting average, bowling average, and team is present in the dataset.

We will make a few visualizations. But first, we will need a few libraries.


```{r}
library(ggplot2)
library(tibble)
```


Let’s load the data the data and convert it to a tibble.


```{r}
cric <- read.csv("battingbowling.csv")
cric <- as_tibble(cric)
cric
```

Let’s create a side-by-side boxplot of the Batting averages:

```{r fig.align='center'}
p <- ggplot(cric, aes(x = Team,y = Batting))
p + geom_boxplot(fill = "tomato")+
labs(title = "Batting Average",
subtitle = "Side-by-side boxplot for Teams",
y = "Batting Average")
```

